---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# means

<!-- badges: start -->
<!-- badges: end -->

The purpose of `means` is to provide the `mean` function with some friends. Especially when the input is very large, users can know the details of what the function is doing during the computation process.

## Installation

You can install the released version of means from [CRAN](https://CRAN.R-project.org) with:


```r
devtools::install_github("emma-wang29/means")
```


## Basic Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(means)

mean_cal(1:9)
```

## Development

Always load devtools package first, as it is the public face of a set of packages that support various aspects of package development.

```{r}
library(devtools)
```

To create this R package, call `create_package()` in the console to initialize a new package. The means directory is an R project, we may want to maunipulate it on GitHub, then use `use_git()`.

```{r}
create_package("~/Desktop/means")

use_git()
```


After the R package is created, we can restart R and make a new R script using `use_r()`, and write a function there: start with `mean_cal()`. Then use `load_all()` and `check()` to make the function available for interactive use and check if the package is intact.

A warning will be occurred after running `check()`, which is related to license. So, we need to edit the license through `use_mit_license()`.

```{r}
use_mit_license("Xuerou Wang")
```

We always use `devtools::document()` to update documentation.

We still want to test the function to see if it works well, then I used `use_testthat()` for the package to create an R script containing tests: `use_testthat("test-meancal")`

Then check all tests with `test()` in the console to see if it passes the test. Also, I want to test the package using `gapminder` dataset, so I use `::` to access `gapminder`, which added in the `DESCRIPTION` file under `Imports`.

```{r}
mean_cal(gapminder::gapminder$gdpPercap)
```

To make the R package more readable, README is added through:
```{r}
use_readme_rmd()
```

and render it everytime with `build_readme()`.


Finally, make a vignette with:

```{r}
use_vignette("means")
```

And, build all vignettes with:
```{r}
build_vignettes()
```











